---
title: "mediation_DMR_DMP_final_pretty"
author: "Katharina Mattonet"
date: "9 M雷z 2021"
output: html_document
---

# load libraries

```{r libraries}
library(caret)
library(dplyr)
library(lme4)
library(lavaan)
library(semPlot)
library(semTools)
library(MASS)
library(Hmisc)
library(regsem)
library(IlluminaHumanMethylationEPICanno.ilm10b2.hg19)
```

# load data

```{r data}

#load("path/mediation_WGCNA_IQ_image_N142_nonlog.RData")

load("path/github/mVal_github.RData")
load("path/pheno_data_N144_github.RData")

load("path/celltypes_estimates_github.RData")

load(file = "path/BayleyU2U4_HAWIKU7_age_predicted_nonlog.RData")

eigenCpGs <- readRDS(file = "path/wagcna_eigencpgs_fsub.rds")

hubCpG <- readRDS(file = "path/tophub_fsub2.rds")

load("path/top_modules_f_pcdf130_round_CI.RData")
```

# subset data sex-combined

```{r subset data}

# sex combined

## create data set to analyse

pheno_data <- cbind(pheno_data, ct_estimate[,c("CD4T", "NK", "Mono", "CD8T", "Gran", "Bcell")])

IQ <- data.frame(as.integer(cogDev_age_predicted$D_StdNr), cogDev_age_predicted$predict_HAWIK_IQ_mixed)
colnames(IQ) <- c("D_StdNr", "IQ_mixed")
pheno_data <- left_join(pheno_data, IQ, by = "D_StdNr")
pheno_data$AMP_Plate <- factor(pheno_data$AMP_Plate, levels = c("WG6975702-MSA4", "WG6975703-MSA4"), labels = c(0,1))
pheno_data <- pheno_data[ !(pheno_data$D_StdNr %in% c(157, 55)), ]
pheno_data$sex_n <- as.numeric(levels(pheno_data$sex_n))[pheno_data$sex_n]
pheno_data$PCDF130c <- scale(pheno_data$PCDF130, center = TRUE, scale = FALSE)


mVal <- mVals_noNA_df
mVal$`55` <- NULL
mVal$`157` <- NULL

hubCpG <- data.frame(hubCpG)
hubCpG$module <- rownames(hubCpG)
rownames(hubCpG) <- c(1:173)

```

# eigenCpG in WGCNA-modules only females

```{r eigenCpG in modules}

eigenCpGs_df <- data.frame(eigenCpGs[["eigengenes"]])
eigenCpGs_sigmodule_f <- eigenCpGs_df[,((colnames(eigenCpGs_df)) %in% top_modules_f_pcdf130_round$modules)]

sigGO_modules_f <- c("MEbrown", "MElightcyan1", "MEred", "MEsalmon", "MEwhite", "MEyellow")
eigenCpGs_sigGO_f <- eigenCpGs_df[,((colnames(eigenCpGs_df)) %in% sigGO_modules_f)]
eigenCpGs_sigGO_f$D_StdNr <- as.integer(rownames(eigenCpGs_sigGO_f))

pheno_data_f <- pheno_data[pheno_data$sex_n == 0,]

pheno_data_f <- left_join(pheno_data_f, eigenCpGs_sigGO_f, by = "D_StdNr")

```

# hubGpG of WGCNA-modules

```{r hubCpG}
sigGO_modules_fm <- gsub(".*ME","", sigGO_modules_f)

hubCpG_sigGO <- hubCpG[(hubCpG$module %in% sigGO_modules_fm), ]

#hubCpG_M <- mVal[hubCpG_sigGO$hubCpG,]
#hubCpG_M_wrong <- hubCpG_M
hubCpG_M <- mVal[rownames(mVal) %in% hubCpG_sigGO$hubCpG,]

hubCpG_M_t <- data.frame(t(hubCpG_M))
pheno_data <- cbind(pheno_data, hubCpG_M_t)
```

# set seed for replication

```{r seed}

set.seed(123)

```

# check data for normal distribution eigenCpG - females only

```{r check data eigenCpG}
var(pheno_data_f$IQ_mixed, na.rm = TRUE) #  8.921538, use IQ_mixed as outcome in main models
length(which(is.na(pheno_data_f$IQ_mixed))) # non

skew(pheno_data_f$IQ_mixed)
kurtosis(pheno_data_f$IQ_mixed)
skew(pheno_data_f$PCDF130c)
kurtosis(pheno_data_f$PCDF130c)
# not normal distributed data

# covariate preselection
corrmatrixY_pcdf130_f <- as.matrix(subset(pheno_data_f, select = c(IQ_mixed, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m)))
rcorr(corrmatrixY_pcdf130_f)$P[, "IQ_mixed"] # p < .05 including in following mediation model

## crate APA-table of correlation matrix
### function
corstarsl <- function(x){
require(Hmisc)
x <- as.matrix(x)
R <- rcorr(x)$r
p <- rcorr(x)$P
p <- round(p, digits = 2)

## define notions for significance levels; spacing is important.
mystars <- ifelse(p < .01, "**", ifelse(p < .05, "*", " "))

## trunctuate the matrix that holds the correlations to two decimal
R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]

## build a new matrix that includes the correlations with their apropriate stars
Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
diag(Rnew) <- paste(diag(R), " ", sep="")
rownames(Rnew) <- colnames(x)
colnames(Rnew) <- paste(colnames(x), "", sep="")

## remove upper triangle
Rnew <- as.matrix(Rnew)
Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
Rnew <- as.data.frame(Rnew)

## remove last column and return the matrix (which is now a data frame)
Rnew <- cbind(Rnew[1:length(Rnew)-1])
return(Rnew)
} 

corrtable <- as.data.frame(corstarsl(corrmatrixY_pcdf130_f)[2:7,1])
colnames(corrtable) <- "child압 cognitive ability\n (N=73)"
rownames(corrtable) <- c("mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy")
corrtable

#write.csv2(corrtable, file = "path/mediation_WGCNA_corrtable_covvarIQnonlog_f_N73.csv")

```

# PCDF130 eigenCpG of sig module brown in females only
 
```{r medmodel pcdf130 female eigenCpG brown}

corrmatrixM_pcdf130_brown_f <- as.matrix(subset(pheno_data_f, select = c(MEbrown, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_brown_f)$P[, "MEbrown"] # p < .05 including in following mediation model

corrtable_pcdf130_brown_f <- as.data.frame(corstarsl(corrmatrixM_pcdf130_brown_f)[2:14,1])
colnames(corrtable_pcdf130_brown_f) <- "eigenCpG (brown module)"
rownames(corrtable_pcdf130_brown_f) <- c("mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")

skew(pheno_data_f$MEbrown)
kurtosis(pheno_data_f$MEbrown)

model_pcdf130_brown_feeee <- '
          IQ_mixed ~ c*PCDF130 + b*MEbrown + dur_gest + BMI_m + Bcell + AMP_Plate
          MEbrown ~ a*PCDF130 + dur_gest + BMI_m + Bcell + AMP_Plate
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_brown_f.fit.YBeeee <- sem(model_pcdf130_brown_feeee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_brown_f.fit.YBeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_brown_feee <- '
          IQ_mixed ~ c*PCDF130 + b*MEbrown + BMI_m + Bcell + AMP_Plate
          MEbrown ~ a*PCDF130 + BMI_m + Bcell + AMP_Plate
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_brown_f.fit.YBeee <- sem(model_pcdf130_brown_feee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_brown_f.fit.YBeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_brown_fee <- '
          IQ_mixed ~ c*PCDF130 + b*MEbrown + Bcell + AMP_Plate
          MEbrown ~ a*PCDF130 + Bcell + AMP_Plate
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_brown_f.fit.YBee <- sem(model_pcdf130_brown_fee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_brown_f.fit.YBee, fit = TRUE, rsquar = TRUE)

# final model 
model_pcdf130_brown_f <- '
          IQ_mixed ~ c*PCDF130 + b*MEbrown + BMI_m + Bcell + AMP_Plate
          MEbrown ~ a*PCDF130 + BMI_m + Bcell + AMP_Plate
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_brown_f.fit.YB <- sem(model_pcdf130_brown_f, data = pheno_data_f, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_brown_f.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_brown_f.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# PCDF130 eigenCpG of sig module lightcyan1 in females only
 
```{r medmodel pcdf130 female eigenCpG lightcyan1}

corrmatrixM_pcdf130_lightcyan1_f <- as.matrix(subset(pheno_data_f, select = c(MElightcyan1, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_lightcyan1_f)$P[, "MElightcyan1"] # p < .05 including in following mediation model

corrtable_pcdf130_lightcyan1_f <- as.data.frame(corstarsl(corrmatrixM_pcdf130_lightcyan1_f)[2:14,1])
colnames(corrtable_pcdf130_lightcyan1_f) <- "eigenCpG (lightcyan1 module)"
rownames(corrtable_pcdf130_lightcyan1_f) <- c("mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")
corrtable_covvareigenCpG <- cbind(corrtable_pcdf130_brown_f, corrtable_pcdf130_lightcyan1_f)

skew(pheno_data_f$MElightcyan1)
kurtosis(pheno_data_f$MElightcyan1)

#model selection
model_pcdf130_lightcyan1_feeeee <- '
          IQ_mixed ~ c*PCDF130 + b*MElightcyan1 + BMI_m + dur_gest + CD4T + Gran + Bcell
          MElightcyan1 ~ a*PCDF130 + BMI_m + dur_gest + CD4T + Gran + Bcell
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_lightcyan1_f.fit.YBeeeee <- sem(model_pcdf130_lightcyan1_feeeee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_lightcyan1_f.fit.YBeeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_lightcyan1_feeee <- '
          IQ_mixed ~ c*PCDF130 + b*MElightcyan1 + BMI_m + dur_gest + CD4T + Gran
          MElightcyan1 ~ a*PCDF130 + BMI_m + dur_gest + CD4T + Gran
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_lightcyan1_f.fit.YBeeee <- sem(model_pcdf130_lightcyan1_feeee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_lightcyan1_f.fit.YBeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_lightcyan1_feee <- '
          IQ_mixed ~ c*PCDF130 + b*MElightcyan1 + BMI_m + dur_gest + CD4T
          MElightcyan1 ~ a*PCDF130 + BMI_m + dur_gest + CD4T
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_lightcyan1_f.fit.YBeee <- sem(model_pcdf130_lightcyan1_feee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_lightcyan1_f.fit.YBeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_lightcyan1_fee <- '
          IQ_mixed ~ c*PCDF130 + b*MElightcyan1 + BMI_m + CD4T
          MElightcyan1 ~ a*PCDF130 + BMI_m + CD4T
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_lightcyan1_f.fit.YBee <- sem(model_pcdf130_lightcyan1_fee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_lightcyan1_f.fit.YBee, fit = TRUE, rsquar = TRUE)


# final model 
model_pcdf130_lightcyan1_f <- '
          IQ_mixed ~ c*PCDF130 + b*MElightcyan1 + CD4T
          MElightcyan1 ~ a*PCDF130 + CD4T
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_lightcyan1_f.fit.YB <- sem(model_pcdf130_lightcyan1_f, data = pheno_data_f, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_lightcyan1_f.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_lightcyan1_f.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# PCDF130 eigenCpG of sig module red in females only

```{r medmodel pcdf130 female eigenCpG red}

corrmatrixM_pcdf130_red_f <- as.matrix(subset(pheno_data_f, select = c(MEred, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_red_f)$P[, "MEred"] # p < .05 including in following mediation model

corrtable_pcdf130_red_f <- as.data.frame(corstarsl(corrmatrixM_pcdf130_red_f)[2:14,1])
colnames(corrtable_pcdf130_red_f) <- "eigenCpG (red module)"
rownames(corrtable_pcdf130_red_f) <- c("mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")
corrtable_covvareigenCpG <- cbind(corrtable_covvareigenCpG, corrtable_pcdf130_red_f)

skew(pheno_data_f$MEred)
kurtosis(pheno_data_f$MEred)

# model selection
model_pcdf130_red_feee <- '
          IQ_mixed ~ c*PCDF130 + b*MEred + dur_gest + BMI_m + AMP_Plate
          MEred ~ a*PCDF130 + BMI_m + dur_gest + AMP_Plate
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_red_f.fit.YBeee <- sem(model_pcdf130_red_feee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_red_f.fit.YBeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_red_fee <- '
          IQ_mixed ~ c*PCDF130 + b*MEred + BMI_m + AMP_Plate
          MEred ~ a*PCDF130 + BMI_m + AMP_Plate
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_red_f.fit.YBee <- sem(model_pcdf130_red_fee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_red_f.fit.YBee, fit = TRUE, rsquar = TRUE)

# final model
model_pcdf130_red_f <- '
          IQ_mixed ~ c*PCDF130 + b*MEred + BMI_m + AMP_Plate
          MEred ~ a*PCDF130 + BMI_m + AMP_Plate
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_red_f.fit.YB <- sem(model_pcdf130_red_f, data = pheno_data_f, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_red_f.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_red_f.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# PCDF130 eigenCpG of sig module salmon in females only

```{r medmodel pcdf130 female eigenCpG salmon}

corrmatrixM_pcdf130_salmon_f <- as.matrix(subset(pheno_data_f, select = c(MEsalmon, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_salmon_f)$P[, "MEsalmon"] # p < .05 including in following mediation model

corrtable_pcdf130_salmon_f <- as.data.frame(corstarsl(corrmatrixM_pcdf130_salmon_f)[2:14,1])
colnames(corrtable_pcdf130_salmon_f) <- "eigenCpG (salmon module)"
rownames(corrtable_pcdf130_salmon_f) <- c("mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")
corrtable_covvareigenCpG <- cbind(corrtable_covvareigenCpG, corrtable_pcdf130_salmon_f)

skew(pheno_data_f$MEsalmon)
kurtosis(pheno_data_f$MEsalmon)

# model selection
model_pcdf130_salmon_feee <- '
          IQ_mixed ~ c*PCDF130 + b*MEsalmon + dur_gest + BMI_m + AMP_Plate
          MEsalmon ~ a*PCDF130 + dur_gest + BMI_m + AMP_Plate
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_salmon_f.fit.YBeee <- sem(model_pcdf130_salmon_feee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_salmon_f.fit.YBeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_salmon_fee <- '
          IQ_mixed ~ c*PCDF130 + b*MEsalmon + BMI_m + AMP_Plate
          MEsalmon ~ a*PCDF130 + BMI_m + AMP_Plate
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_salmon_f.fit.YBee <- sem(model_pcdf130_salmon_fee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_salmon_f.fit.YBee, fit = TRUE, rsquar = TRUE)

# final model
model_pcdf130_salmon_f <- '
          IQ_mixed ~ c*PCDF130 + b*MEsalmon + BMI_m + AMP_Plate
          MEsalmon ~ a*PCDF130 + BMI_m + AMP_Plate
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_salmon_f.fit.YB <- sem(model_pcdf130_salmon_f, data = pheno_data_f, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_salmon_f.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_salmon_f.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# PCDF130 eigenCpG of sig module white in females only

```{r medmodel pcdf130 female eigenCpG white}

corrmatrixM_pcdf130_white_f <- as.matrix(subset(pheno_data_f, select = c(MEwhite, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_white_f)$P[, "MEwhite"] # p < .05 including in following mediation model

corrtable_pcdf130_white_f <- as.data.frame(corstarsl(corrmatrixM_pcdf130_white_f)[2:14,1])
colnames(corrtable_pcdf130_white_f) <- "eigenCpG (white module)"
rownames(corrtable_pcdf130_white_f) <- c("mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")
corrtable_covvareigenCpG <- cbind(corrtable_covvareigenCpG, corrtable_pcdf130_white_f)


skew(pheno_data_f$MEwhite)
kurtosis(pheno_data_f$MEwhite)

# model selection
model_pcdf130_white_feeeee <- '
          IQ_mixed ~ c*PCDF130 + b*MEwhite + BMI_m + dur_gest + CD4T + Gran + Bcell
          MEwhite ~ a*PCDF130 + BMI_m + dur_gest + CD4T + Gran + Bcell
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_white_f.fit.YBeeeee <- sem(model_pcdf130_white_feeeee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_white_f.fit.YBeeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_white_feeee <- '
          IQ_mixed ~ c*PCDF130 + b*MEwhite + BMI_m + dur_gest + Gran + Bcell
          MEwhite ~ a*PCDF130 + BMI_m + dur_gest + Gran + Bcell
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_white_f.fit.YBeeee <- sem(model_pcdf130_white_feeee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_white_f.fit.YBeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_white_feee <- '
          IQ_mixed ~ c*PCDF130 + b*MEwhite + BMI_m + dur_gest + Bcell
          MEwhite ~ a*PCDF130 + BMI_m + dur_gest + Bcell
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_white_f.fit.Yeee <- sem(model_pcdf130_white_feee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_white_f.fit.Yeee, fit = TRUE, rsquar = TRUE)

# final model
model_pcdf130_white_f <- '
          IQ_mixed ~ c*PCDF130 + b*MEwhite + dur_gest + Bcell
          MEwhite ~ a*PCDF130 + dur_gest + Bcell
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_white_f.fit.YB <- sem(model_pcdf130_white_f, data = pheno_data_f, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_white_f.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_white_f.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# PCDF130 eigenCpG of sig module yellow in females only

```{r medmodel pcdf130 female eigenCpG yellow}

corrmatrixM_pcdf130_yellow_f <- as.matrix(subset(pheno_data_f, select = c(MEyellow, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_yellow_f)$P[, "MEyellow"] # p < .05 including in following mediation model

corrtable_pcdf130_yellow_f <- as.data.frame(corstarsl(corrmatrixM_pcdf130_yellow_f)[2:14,1])
colnames(corrtable_pcdf130_yellow_f) <- "eigenCpG (yellow module)"
rownames(corrtable_pcdf130_yellow_f) <- c("mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")
corrtable_covvareigenCpG <- cbind(corrtable_covvareigenCpG, corrtable_pcdf130_yellow_f)

#write.csv2(corrtable_covvareigenCpG, file = "path/mediation_WGCNA_corrtable_covvareigenCpG_f_N73.csv")

skew(pheno_data_f$MEyellow)
kurtosis(pheno_data_f$MEyellow)

# model selection
model_pcdf130_yellow_feee <- '
          IQ_mixed ~ c*PCDF130 + b*MEyellow + dur_gest + BMI_m + Bcell
          MEyellow ~ a*PCDF130 + dur_gest + BMI_m + Bcell
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_yellow_f.fit.YBeee <- sem(model_pcdf130_yellow_feee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_yellow_f.fit.YBeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_yellow_fee <- '
          IQ_mixed ~ c*PCDF130 + b*MEyellow + BMI_m + Bcell
          MEyellow ~ a*PCDF130 + BMI_m + Bcell
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_yellow_f.fit.YBee <- sem(model_pcdf130_yellow_fee, data = pheno_data_f, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_yellow_f.fit.YBee, fit = TRUE, rsquar = TRUE)

# final model
model_pcdf130_yellow_f <- '
          IQ_mixed ~ c*PCDF130 + b*MEyellow + Bcell
          MEyellow ~ a*PCDF130 + Bcell
		      indirect := a*b
		      total := c + indirect' 
model_pcdf130_yellow_f.fit.YB <- sem(model_pcdf130_yellow_f, data = pheno_data_f, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_yellow_f.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_yellow_f.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# check data for normal distribution hubCpG - both sexes 

```{r check data hubCpG}
var(pheno_data$IQ_mixed, na.rm = TRUE) #  12.68551, use IQ_mixed as outcome in main models
length(which(is.na(pheno_data$IQ_mixed))) # yes N = 2 

skew(pheno_data$IQ_mixed)
kurtosis(pheno_data$IQ_mixed)
skew(pheno_data$PCDF130c)
kurtosis(pheno_data$PCDF130c)

# covariate preselection
corrmatrixY_pcdf130 <- as.matrix(subset(pheno_data, select = c(IQ_mixed, sex_n, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m)))
rcorr(corrmatrixY_pcdf130)$P[, "IQ_mixed"] # p < .05 including in following mediation model

corrtable_all <- as.data.frame(corstarsl(corrmatrixY_pcdf130)[2:8,1])
colnames(corrtable_all) <- "child압 cognitive ability\n (N=142)"
rownames(corrtable_all) <- c("neonate압 sex", "mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy")

#write.csv2(corrtable_all, file = "path/mediation_WGCNA_corrtable_covvarIQnonlog_all_N142.csv")

```

# PCDF130 hubCpG of sig modules brown

```{r medmodel hubCpG brown}

corrmatrixM_pcdf130_cg09899564 <- as.matrix(subset(pheno_data, select = c(cg09899564, sex_n, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_cg09899564)$P[, "cg09899564"] # p < .05 including in following mediation model

corrtable_pcdf130_brown_hubCpG <- as.data.frame(corstarsl(corrmatrixM_pcdf130_cg09899564)[2:15,1])
colnames(corrtable_pcdf130_brown_hubCpG) <- "hubCpG (brown module)"
rownames(corrtable_pcdf130_brown_hubCpG) <- c("neonate압 sex", "mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")

skew(pheno_data$cg09899564)
kurtosis(pheno_data$cg09899564)

model_pcdf130_cg09899564eeeeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg09899564 + dur_gest + weight_n + BMI_m + CD4T + Mono + NK + Gran + Bcell
          cg09899564 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + dur_gest + weight_n + BMI_m + CD4T + Mono + NK + Gran + Bcell
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1
          ' 
model_pcdf130_cg09899564.fit.YBeeeeee <- sem(model_pcdf130_cg09899564eeeeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg09899564.fit.YBeeeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg09899564eeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg09899564 + weight_n + BMI_m + CD4T + Mono + NK + Gran + Bcell
          cg09899564 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + Mono + NK + Gran + Bcell
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1
          ' 
model_pcdf130_cg09899564.fit.YBeeee <- sem(model_pcdf130_cg09899564eeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg09899564.fit.YBeeee, fit = TRUE, rsquar = TRUE)

# final model
model_pcdf130_cg09899564 <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg09899564 + weight_n + BMI_m + CD4T + Mono + NK + Gran + Bcell
          cg09899564 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + Mono + NK + Gran + Bcell
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1
          ' 
model_pcdf130_cg09899564.fit.YB <- sem(model_pcdf130_cg09899564, data = pheno_data, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg09899564.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_cg09899564.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# PCDF130 hubCpG of sig modules lightcyan1

```{r medmodel hubCpG lightcyan1}

# covariate preselection

corrmatrixM_pcdf130_cg11468953 <- as.matrix(subset(pheno_data, select = c(cg11468953, sex_n, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_cg11468953)$P[, "cg11468953"] # p < .05 including in following mediation model

corrtable_pcdf130_lightcyan1_hubCpG <- as.data.frame(corstarsl(corrmatrixM_pcdf130_cg11468953)[2:15,1])
colnames(corrtable_pcdf130_lightcyan1_hubCpG) <- "hubCpG (lightcyan1 module)"
rownames(corrtable_pcdf130_lightcyan1_hubCpG) <- c("neonate압 sex", "mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")
corrtable_covvarhubCpG <- cbind(corrtable_pcdf130_brown_hubCpG, corrtable_pcdf130_lightcyan1_hubCpG)

skew(pheno_data$cg11468953)
kurtosis(pheno_data$cg11468953)

# model selection
model_pcdf130_cg11468953eeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg11468953 + dur_gest + weight_n + BMI_m + CD4T + Mono + NK + Gran + Bcell
          cg11468953 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + dur_gest + weight_n + BMI_m + CD4T + Mono + NK + Gran + Bcell
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg11468953.fit.YBeeee <- sem(model_pcdf130_cg11468953eeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg11468953.fit.YBeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg11468953eee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg11468953 + weight_n + BMI_m + CD4T + Mono + NK + Bcell
          cg11468953 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + Mono + NK + Bcell
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg11468953.fit.YBeee <- sem(model_pcdf130_cg11468953eee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg11468953.fit.YBeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg11468953ee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg11468953 + weight_n + BMI_m + CD4T + Mono + Bcell
          cg11468953 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + Mono + Bcell
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg11468953.fit.YBee <- sem(model_pcdf130_cg11468953ee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg11468953.fit.YBee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg11468953e <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg11468953 + weight_n + BMI_m + CD4T + Bcell
          cg11468953 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + Bcell
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg11468953.fit.YBe <- sem(model_pcdf130_cg11468953e, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg11468953.fit.YBe, fit = TRUE, rsquar = TRUE)

# final model
model_pcdf130_cg11468953 <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg11468953 + weight_n + BMI_m + CD4T + Bcell
          cg11468953 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + Bcell
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg11468953.fit.YB <- sem(model_pcdf130_cg11468953, data = pheno_data, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg11468953.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_cg11468953.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# PCDF130 hubCpG of sig modules red

```{r medmodel hubCpG red}

# covariate preselection

corrmatrixM_pcdf130_cg18901378 <- as.matrix(subset(pheno_data, select = c(cg18901378, sex_n, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_cg18901378)$P[, "cg18901378"] # p < .05 including in following mediation model

corrtable_pcdf130_red_hubCpG <- as.data.frame(corstarsl(corrmatrixM_pcdf130_cg18901378)[2:15,1])
colnames(corrtable_pcdf130_red_hubCpG) <- "hubCpG (red module)"
rownames(corrtable_pcdf130_red_hubCpG) <- c("neonate압 sex", "mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")
corrtable_covvarhubCpG <- cbind(corrtable_covvarhubCpG, corrtable_pcdf130_red_hubCpG)

skew(pheno_data$cg18901378)
kurtosis(pheno_data$cg18901378)

# model selection
model_pcdf130_cg18901378eeeeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg18901378 + dur_gest + weight_n + BMI_m + age_m + AMP_Plate
          cg18901378 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + dur_gest + weight_n + BMI_m + age_m + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg18901378.fit.YBeeeeee <- sem(model_pcdf130_cg18901378eeeeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg18901378.fit.YBeeeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg18901378eeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg18901378 + weight_n + BMI_m + age_m + AMP_Plate
          cg18901378 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + age_m + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg18901378.fit.YBeeee <- sem(model_pcdf130_cg18901378eeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg18901378.fit.YBeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg18901378eee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg18901378 + weight_n + BMI_m + AMP_Plate
          cg18901378 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg18901378.fit.YBeee <- sem(model_pcdf130_cg18901378eee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg18901378.fit.YBeee, fit = TRUE, rsquar = TRUE)

# final model
model_pcdf130_cg18901378 <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg18901378 + weight_n + BMI_m + AMP_Plate
          cg18901378 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg18901378.fit.YB <- sem(model_pcdf130_cg18901378, data = pheno_data, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg18901378.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_cg18901378.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# PCDF130 hubCpG of sig modules salmon


```{r medmodel hubCpG salmon}

# covariate preselection

corrmatrixM_pcdf130_cg01733928 <- as.matrix(subset(pheno_data, select = c(cg01733928, sex_n, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_cg01733928)$P[, "cg01733928"] # p < .05 including in following mediation model

corrtable_pcdf130_salmon_hubCpG <- as.data.frame(corstarsl(corrmatrixM_pcdf130_cg01733928)[2:15,1])
colnames(corrtable_pcdf130_salmon_hubCpG) <- "hubCpG (salmon module)"
rownames(corrtable_pcdf130_salmon_hubCpG) <- c("neonate압 sex", "mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")
corrtable_covvarhubCpG <- cbind(corrtable_covvarhubCpG, corrtable_pcdf130_salmon_hubCpG)


skew(pheno_data$cg01733928)
kurtosis(pheno_data$cg01733928)

# model selection
model_pcdf130_cg01733928eeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg01733928 + dur_gest + weight_n + BMI_m + age_m + Bcell + AMP_Plate
          cg01733928 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + dur_gest + weight_n + BMI_m + age_m + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg01733928.fit.YBeeee <- sem(model_pcdf130_cg01733928eeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg01733928.fit.YBeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg01733928eee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg01733928 + weight_n + BMI_m + age_m + Bcell + AMP_Plate
          cg01733928 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + age_m + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg01733928.fit.YBeee <- sem(model_pcdf130_cg01733928eee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg01733928.fit.YBeee, fit = TRUE, rsquar = TRUE)

# final model
model_pcdf130_cg01733928 <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg01733928 + weight_n + BMI_m + age_m + Bcell + AMP_Plate
          cg01733928 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + age_m + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg01733928.fit.YB <- sem(model_pcdf130_cg01733928, data = pheno_data, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg01733928.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_cg01733928.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# PCDF130 hubCpG of sig modules white


```{r medmodel hubCpG white}

# covariate preselection

corrmatrixM_pcdf130_cg10482044 <- as.matrix(subset(pheno_data, select = c(cg10482044
, sex_n, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_cg10482044)$P[, "cg10482044"] # p < .05 including in following mediation model

corrtable_pcdf130_white_hubCpG <- as.data.frame(corstarsl(corrmatrixM_pcdf130_cg10482044)[2:15,1])
colnames(corrtable_pcdf130_white_hubCpG) <- "hubCpG (white module)"
rownames(corrtable_pcdf130_white_hubCpG) <- c("neonate압 sex", "mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")
corrtable_covvarhubCpG <- cbind(corrtable_covvarhubCpG, corrtable_pcdf130_white_hubCpG)

skew(pheno_data$cg10482044)
kurtosis(pheno_data$cg10482044)

# model selection
model_pcdf130_cg10482044eeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg10482044 + dur_gest + weight_n + BMI_m + highEduc_m_r + CD4T + NK + Gran + Bcell + AMP_Plate
          cg10482044 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + dur_gest + weight_n + BMI_m + highEduc_m_r + CD4T + NK + Gran + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg10482044.fit.YBeeee <- sem(model_pcdf130_cg10482044eeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg10482044.fit.YBeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg10482044eee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg10482044 + weight_n + BMI_m + highEduc_m_r + CD4T + NK + Gran + Bcell + AMP_Plate
          cg10482044 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + highEduc_m_r + CD4T + NK + Gran + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg10482044.fit.YBeee <- sem(model_pcdf130_cg10482044eee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg10482044.fit.YBeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg10482044ee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg10482044 + weight_n + BMI_m + CD4T + NK + Gran + Bcell + AMP_Plate
          cg10482044 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + NK + Gran + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg10482044.fit.YBee <- sem(model_pcdf130_cg10482044ee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg10482044.fit.YBee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg10482044_e <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg10482044 + weight_n + BMI_m + CD4T + Bcell + AMP_Plate
          cg10482044 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg10482044.fit.YB_e <- sem(model_pcdf130_cg10482044_e, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg10482044.fit.YB_e, fit = TRUE, rsquar = TRUE)

# final model
model_pcdf130_cg10482044 <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg10482044 + weight_n + BMI_m + CD4T + Bcell + AMP_Plate
          cg10482044 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1'
model_pcdf130_cg10482044.fit.YB <- sem(model_pcdf130_cg10482044, data = pheno_data, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg10482044.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_cg10482044.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# PCDF130 hubCpG of sig modules yellow


```{r medmodel hubCpG yellow}

# covariate preselection

corrmatrixM_pcdf130_cg09941484 <- as.matrix(subset(pheno_data, select = c(cg09941484
, sex_n, age_m, dur_gest, smoke_m_r, weight_n, highEduc_m_r, BMI_m, CD4T, CD8T, Mono, NK, Gran, Bcell, AMP_Plate)))
rcorr(corrmatrixM_pcdf130_cg09941484)$P[, "cg09941484"] # p < .05 including in following mediation model

corrtable_pcdf130_yellow_hubCpG <- as.data.frame(corstarsl(corrmatrixM_pcdf130_cg09941484)[2:15,1])
colnames(corrtable_pcdf130_yellow_hubCpG) <- "hubCpG (yellow module)"
rownames(corrtable_pcdf130_yellow_hubCpG) <- c("neonate압 sex", "mother압 age at birth", "gestational length", "mother압 smoking status during pregnancy", "neonate압 birth weight", "mother압 education level", "mother압 BMI before pregnancy", "CD4T fraction", "CD8T fraction", "monocyte fraction", "NK fraction", "granulocyte fraction", "Bcell fraction", "EPIC assay plate")
corrtable_covvarhubCpG <- cbind(corrtable_covvarhubCpG, corrtable_pcdf130_yellow_hubCpG)

#write.csv2(corrtable_covvarhubCpG, file = "path/mediation_WGCNA_corrtable_covvarhubCpG_all_N142.csv")

skew(pheno_data$cg09941484)
kurtosis(pheno_data$cg09941484)

#model selection
model_pcdf130_cg09941484eeeeeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg09941484 + dur_gest + weight_n + BMI_m + smoke_m_r + CD4T + Mono + NK + Gran + Bcell + AMP_Plate
          cg09941484 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + dur_gest + weight_n + BMI_m + smoke_m_r + CD4T + Mono + NK + Gran + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg09941484.fit.YBeeeeeee <- sem(model_pcdf130_cg09941484eeeeeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg09941484.fit.YBeeeeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg09941484eeeeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg09941484 + weight_n + BMI_m + smoke_m_r + CD4T + Mono + NK + Gran + Bcell + AMP_Plate
          cg09941484 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + smoke_m_r + CD4T + Mono + NK + Gran + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg09941484.fit.YBeeeeee <- sem(model_pcdf130_cg09941484eeeeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg09941484.fit.YBeeeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg09941484eeeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg09941484 + weight_n + BMI_m + CD4T + Mono + NK + Gran + Bcell + AMP_Plate
          cg09941484 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m +  CD4T + Mono + NK + Gran + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg09941484.fit.YBeeeee <- sem(model_pcdf130_cg09941484eeeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg09941484.fit.YBeeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg09941484eeee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg09941484 + weight_n + BMI_m + CD4T + NK + Gran + Bcell + AMP_Plate
          cg09941484 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + NK + Gran + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg09941484.fit.YBeeee <- sem(model_pcdf130_cg09941484eeee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg09941484.fit.YBeeee, fit = TRUE, rsquar = TRUE)

model_pcdf130_cg09941484eee <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg09941484 + weight_n + BMI_m + CD4T + Gran + Bcell + AMP_Plate
          cg09941484 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + Gran + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg09941484.fit.YBeee <- sem(model_pcdf130_cg09941484eee, data = pheno_data, se = "bootstrap", test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg09941484.fit.YBeee, fit = TRUE, rsquar = TRUE)

# final model
model_pcdf130_cg09941484 <- '
          IQ_mixed ~ c*PCDF130c + sex_n + cw*PCDF130c:sex_n + b*cg09941484 + weight_n + BMI_m + CD4T + Gran + Bcell + AMP_Plate
          cg09941484 ~ a*PCDF130c + sex_n + aw*PCDF130c:sex_n + weight_n + BMI_m + CD4T + Gran + Bcell + AMP_Plate
		      indirect0 := a*b # + 0*aw*b
		      total0 := c + indirect0 # + 0*cw
          indirect1 := indirect0 + 1*aw*b
          total1 := c + indirect1 + 1*cw
          diffind := indirect0 - indirect1
          difftotal := total0 - total1' 
model_pcdf130_cg09941484.fit.YB <- sem(model_pcdf130_cg09941484, data = pheno_data, se = "bootstrap", bootstrap = 10000, test = "yuan.bentler", missing = "fiml.x")
summary(model_pcdf130_cg09941484.fit.YB, fit = TRUE, rsquar = TRUE)
parameterEstimates(model_pcdf130_cg09941484.fit.YB, ci = T, boot.ci.type = "bca.simple")

```

# export results to tables (& figures)

```{r export results}

l_pcdf130_brown_f <- parameterEstimates(model_pcdf130_brown_f.fit.YB)[c(1:9, 13:15, 17:18, 20), ]
l_pcdf130_brown_f
b_pcdf130_brown_f <- gettextf('%s %.2f p=%.2f', l_pcdf130_brown_f$label, l_pcdf130_brown_f$est, digits = l_pcdf130_brown_f$pvalue)
b_pcdf130_brown_f <- gsub(".*p=NA.*", "", b_pcdf130_brown_f)
b_pcdf130_brown_f <- gsub("w", "*sex", b_pcdf130_brown_f)
b_pcdf130_brown_f
semPaths(model_pcdf130_brown_f.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_brown_f.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_brown_f, label.prop = 1,  edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "EigenCpG\nbrown", "PCDF130", "mother압\nBMI\nbefore\npregnancy", "B-cells", "EPIC\narray\nplate"), edge.label.position = .7, edge.width = .6, node.width = 1.5, curve = 2)

l_pcdf130_lightcyan1_f <- parameterEstimates(model_pcdf130_lightcyan1_f.fit.YB)[c(1:10), ]
l_pcdf130_lightcyan1_f
b_pcdf130_lightcyan1_f <- gettextf('%s %.2f\np=%.2f', l_pcdf130_lightcyan1_f$label, l_pcdf130_lightcyan1_f$est, digits = l_pcdf130_lightcyan1_f$pvalue)
b_pcdf130_lightcyan1_f <- gsub("\np=NA", "", b_pcdf130_lightcyan1_f)
b_pcdf130_lightcyan1_f <- gsub("w", "*sex", b_pcdf130_lightcyan1_f)
b_pcdf130_lightcyan1_f
semPaths(model_pcdf130_lightcyan1_f.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_lightcyan1_f.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_lightcyan1_f, label.prop = 1,  edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "EigenCpG\nlightcyan1", "PCDF130", "CD4T"), edge.label.position = .7, edge.width = .6, node.width = 1.5, curve = 2)

l_pcdf130_red_f <- parameterEstimates(model_pcdf130_red_f.fit.YB)[c(1:7, 11:12, 14), ]
l_pcdf130_red_f
b_pcdf130_red_f <- gettextf('%s %.2f\np=%.2f', l_pcdf130_red_f$label, l_pcdf130_red_f$est, digits = l_pcdf130_red_f$pvalue)
b_pcdf130_red_f <- gsub(".*p=NA.*", "", b_pcdf130_red_f)
b_pcdf130_red_f <- gsub("w", "*sex", b_pcdf130_red_f)
b_pcdf130_red_f
semPaths(model_pcdf130_red_f.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_red_f.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_red_f, label.prop = 1,  edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "EigenCpG\nred", "PCDF130", "mother압\nBMI\nbefore\npregnancy", "EPIC\narray\nplate"), edge.label.position = .7, edge.width = .6, node.width = 1.5, curve = 2)

l_pcdf130_salmon_f <- parameterEstimates(model_pcdf130_salmon_f.fit.YB)[c(1:7, 11:12, 14), ]
l_pcdf130_salmon_f
b_pcdf130_salmon_f <- gettextf('%s %.2f\np=%.2f', l_pcdf130_salmon_f$label, l_pcdf130_salmon_f$est, digits = l_pcdf130_salmon_f$pvalue)
b_pcdf130_salmon_f <- gsub(".*p=NA.*", "", b_pcdf130_salmon_f)
b_pcdf130_salmon_f <- gsub("w", "*sex", b_pcdf130_salmon_f)
b_pcdf130_salmon_f
semPaths(model_pcdf130_salmon_f.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_salmon_f.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_salmon_f, label.prop = 1,  edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "EigenCpG\nsalmon", "PCDF130", "mother압\nBMI\nbefore\npregnancy", "EPIC\narray\nplate"), edge.label.position = .7, edge.width = .6, node.width = 1.5, curve = 2)

l_pcdf130_white_f <- parameterEstimates(model_pcdf130_white_f.fit.YB)[c(1:7, 11:12, 14), ]
l_pcdf130_white_f
b_pcdf130_white_f <- gettextf('%s %.2f\np=%.2f', l_pcdf130_white_f$label, l_pcdf130_white_f$est, digits = l_pcdf130_white_f$pvalue)
b_pcdf130_white_f <- gsub(".*p=NA.*", "", b_pcdf130_white_f)
b_pcdf130_white_f <- gsub("w", "*sex", b_pcdf130_white_f)
b_pcdf130_white_f
semPaths(model_pcdf130_white_f.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_white_f.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_white_f, label.prop = 1,  edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "EigenCpG\nwhite", "PCDF130", "gestational\nlength", "B-cells"), edge.label.position = .7, edge.width = .6, node.width = 1.5, curve = 2)

l_pcdf130_yellow_f <- parameterEstimates(model_pcdf130_yellow_f.fit.YB)[c(1:10), ]
l_pcdf130_yellow_f
b_pcdf130_yellow_f <- gettextf('%s %.2f\np=%.2f', l_pcdf130_yellow_f$label, l_pcdf130_yellow_f$est, digits = l_pcdf130_yellow_f$pvalue)
b_pcdf130_yellow_f <- gsub("\np=NA", "", b_pcdf130_yellow_f)
b_pcdf130_yellow_f <- gsub("w", "*sex", b_pcdf130_yellow_f)
b_pcdf130_yellow_f
semPaths(model_pcdf130_yellow_f.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_yellow_f.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_yellow_f, label.prop = 1,  edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "EigenCpG\nyellow", "PCDF130", "B-cells"), edge.label.position = .7, edge.width = .6, node.width = 1.5, curve = 2)

l_pcdf130_brown <- parameterEstimates(model_pcdf130_cg09899564.fit.YB)[c(1:21, 25:33, 35:42, 44:50, 52:57, 59:63, 65:68, 70:72, 74:75, 77), ]
l_pcdf130_brown
b_pcdf130_brown <- gettextf('%s %.2f p=%.2f', l_pcdf130_brown$label, l_pcdf130_brown$est, digits = l_pcdf130_brown$pvalue)
b_pcdf130_brown <- gsub(".*p=NA.*", "", b_pcdf130_brown)
b_pcdf130_brown <- gsub("w", "*sex", b_pcdf130_brown)
b_pcdf130_brown
semPaths(model_pcdf130_cg09899564.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_cg09899564.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_brown, edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "hubCpG\nbrown", "PCDF130", "child압\nsex", "PCDF130*\nchild압 sex", "birthweight", "mother압\nBMI\nbefore\npregnancy", "CD4T", "monocytes", "NK", "granulocytes", "B-cells"), edge.label.position = .6, edge.width = .6, node.width = 1.7, curve = 2)

l_pcdf130_lightcyan1 <- parameterEstimates(model_pcdf130_cg11468953.fit.YB)[c(1:15, 19:24, 26:30, 32:35,  37:39, 41:42, 44), ]
l_pcdf130_lightcyan1
b_pcdf130_lightcyan1 <- gettextf('%s %.2f p=%.2f', l_pcdf130_lightcyan1$label, l_pcdf130_lightcyan1$est, digits = l_pcdf130_lightcyan1$pvalue)
b_pcdf130_lightcyan1 <- gsub(".*p=NA.*", "", b_pcdf130_lightcyan1)
b_pcdf130_lightcyan1 <- gsub("w", "*sex", b_pcdf130_lightcyan1)
b_pcdf130_lightcyan1
semPaths(model_pcdf130_cg11468953.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_cg11468953.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_lightcyan1, edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "hubCpG\nlightcyan1", "PCDF130", "child압\nsex", "PCDF130*\nchild압 sex", "birthweight", "mother압\nBMI\nbefore\npregnancy", "CD4T", "B-cells"), edge.label.position = .6, edge.width = .6, node.width = 1.7, curve = 2)

l_pcdf130_red <- parameterEstimates(model_pcdf130_cg18901378.fit.YB)[c(1:13, 17:21, 23:26, 28:30, 32:33, 35), ]
l_pcdf130_red
b_pcdf130_red <- gettextf('%s %.2f p=%.2f', l_pcdf130_red$label, l_pcdf130_red$est, digits = l_pcdf130_red$pvalue)
b_pcdf130_red <- gsub(".*p=NA.*", "", b_pcdf130_red)
b_pcdf130_red <- gsub("w", "*sex", b_pcdf130_red)
b_pcdf130_red
semPaths(model_pcdf130_cg18901378.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_cg18901378.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_red, edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "hubCpG\nred", "PCDF130", "child압\nsex", "PCDF130*\nchild압 sex", "birthweight", "mother압\nBMI\nbefore\npregnancy", "EPIC\narray\nplate"), edge.label.position = .6, edge.width = .6, node.width = 1.7, curve = 2)

l_pcdf130_salmon <- parameterEstimates(model_pcdf130_cg01733928.fit.YB)[c(1:17, 21:27, 29:34, 36:40, 42:45, 47:49, 51:52, 54), ]
l_pcdf130_salmon
b_pcdf130_salmon <- gettextf('%s %.2f p=%.2f', l_pcdf130_salmon$label, l_pcdf130_salmon$est, digits = l_pcdf130_salmon$pvalue)
b_pcdf130_salmon <- gsub(".*p=NA.*", "", b_pcdf130_salmon)
b_pcdf130_salmon <- gsub("w", "*sex", b_pcdf130_salmon)
b_pcdf130_salmon
semPaths(model_pcdf130_cg01733928.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_cg01733928.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_salmon, edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "hubCpG\nsalmon", "PCDF130", "child압\nsex", "PCDF130*\nchild압 sex", "birthweight", "mother압\nBMI\nbefore\npregnancy", "mother압\nage\nat birth", "Bcells", "EPIC\narray\nplate"), edge.label.position = .6, edge.width = .6, node.width = 1.7, curve = 2)

l_pcdf130_white <- parameterEstimates(model_pcdf130_cg10482044.fit.YB)[c(1:17, 21:27, 29:34, 36:40, 42:45, 47:49, 51:52, 54), ]
l_pcdf130_white
b_pcdf130_white <- gettextf('%s %.2f p=%.2f', l_pcdf130_white$label, l_pcdf130_white$est, digits = l_pcdf130_white$pvalue)
b_pcdf130_white <- gsub(".*p=NA.*", "", b_pcdf130_white)
b_pcdf130_white <- gsub("w", "*sex", b_pcdf130_white)
b_pcdf130_white
semPaths(model_pcdf130_cg10482044.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_cg10482044.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_white, edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "hubCpG\nwhite", "PCDF130", "child압\nsex", "PCDF130*\nchild압 sex", "birthweight", "mother압\nBMI\nbefore\npregnancy", "CD4T", "B-cells", "EPIC\narray\nplate"), edge.label.position = .6, edge.width = .6, node.width = 1.7, curve = 2)

l_pcdf130_yellow <- parameterEstimates(model_pcdf130_cg09941484.fit.YB)[c(1:19, 23:30, 32:38, 40:45, 47:51, 53:56, 58:60, 62:63, 65), ]
l_pcdf130_yellow
b_pcdf130_yellow <- gettextf('%s %.2f p=%.2f', l_pcdf130_yellow$label, l_pcdf130_yellow$est, digits = l_pcdf130_yellow$pvalue)
b_pcdf130_yellow <- gsub(".*p=NA.*", "", b_pcdf130_yellow)
b_pcdf130_yellow <- gsub("w", "*sex", b_pcdf130_yellow)
b_pcdf130_yellow
semPaths(model_pcdf130_cg09941484.fit.YB, what= "path", whatLabels = "est", intercepts = FALSE, rotation = 2)
semPaths(model_pcdf130_cg09941484.fit.YB, what = "path", whatLabels = "est", intercepts = FALSE, layout = "tree", rotation = 2, panelGroups = TRUE, edgeLabels = b_pcdf130_yellow, edge.label.bg = TRUE, edge.label.cex = .7, fade = FALSE, nodeLabels = c("child압\ncognitive\nability", "hubCpG\nyellow", "PCDF130", "child압\nsex", "PCDF130*\nchild압 sex", "birthweight", "mother압\nBMI\nbefore\npregnancy", "CD4T", "granulocytes", "B-cells", "EPIC\narray\nplate"), edge.label.position = .6, edge.width = .6, node.width = 1.7, curve = 2)

```

# save

```{r save}

#save.image("path/mediation_WGCNA_IQ_image_N142_nonlog.RData")

```